---
title: "STA426_Exercise_1"
format: 
  html:
    embed-resources: true
editor: visual
---

## Exercise Part B.2

#### 0. Preparation

```{r}
# Delete Workspace
rm(list = ls())

# Import Libraries
library(ggplot2)
library(gridExtra)
```

#### 1. Sampling values from log-normal distribution

In the first step, 100 values are sampled from a log-normal distribution.

```{r}
log_norm <- data.frame(rlnorm(n = 100, meanlog = 5, sdlog = 0.5))
colnames(log_norm) <- c("lognorm")
```

We obtain a sample of 100 values with a sample mean of `r round(mean(log_norm$lognorm),3)` and a sample standard deviation of `r round(sd(log_norm$lognorm),3)`.

#### 2. Plotting the data

Here we plot the sampled data as a histogram.

```{r}
ggplot() +
  geom_histogram(data = log_norm, mapping = aes(x=(lognorm)), 
                 bins = 22) +
  xlab("X") +
  ylab("Density") +
  ggtitle("Histogram of data sampled from lognormal distribution (log-scaled) (N 100)") +
  theme_bw()

```

Here we plot the log-scaled sampled data as a histogram.

```{r}
ggplot() +
  geom_histogram(data = log_norm, mapping = aes(x=log(lognorm)), 
                 bins = 22) +
  xlab("X") +
  ylab("Density") +
  ggtitle("Histogram of data sampled from lognormal distribution (N = 100)") +
  theme_bw()
```

Here we plot the data in violinplots.

```{r}
plot1 <- ggplot(log_norm, mapping = aes(x = "Sample", y = lognorm)) +
  geom_violin() +
  ylab("Value") +
  geom_boxplot(width=0.1) +
  theme_bw() +
  ggtitle("Log-normal Distribution")
  
plot2 <- ggplot(log_norm, mapping = aes(x = "Log-scaled sample", y = log(lognorm))) +
  geom_violin() +
  ylab("Value") +
  geom_boxplot(width=0.1)+
  theme_bw() +
  ggtitle("Log-scaled Log-normal Distribution")
  

grid.arrange(plot1, plot2, ncol=2, nrow = 1)
```
